### 2016-10-05 robust-software.tex
creating section for what we left out

\item
Explain somewhere that there's an 11th rule for compiled languages:
use standard build tools like Make
rather than home-brewed scripts.

@@

@@

Any short list of rules for developing robust software will
necessarily be incomplete.  For example, the rules we present above
are necessary, but not sufficient, for software that needs to interact
with services such as database and web servers.  Such software is
often stopped and started under automatic control, may need to
authenticate, etc., all of which are out of scope of this paper.

Another notable omission is documentation.
We think it is very important for developers to do this,
but our experience is that people are unlikely do it during normal development,
and we don't want to recommend practices that people won't actually adopt.

>>>>

@@

\section*{What We Left Out}

Any short list of rules for developing robust software will
necessarily be incomplete.  A few of our more significant omissions
include:

\begin{description}

\item[\textbf{Services}] The rules we present above are necessary, but
  not sufficient, for software that needs to interact with services
  such as database and web servers.  Such software is often stopped
  and started under automatic control, may need to authenticate, etc.,
  all of which are out of scope of this paper.

\item[\textbf{Documentation}] We think it is very important for
  developers to document their work, but our experience is that people
  are unlikely do it during normal development, and we don't want to
  recommend practices that people won't actually adopt.

\item[\textbf{Build Systems}] If the software depends on a build tool,
  either because it is written in a compiled language or to manage
  workflow, it should use a standard tool such as Make rather than
  home-brewed scripts.

\end{description}

@@
